Artin Group Presentations Arising from Cluster Algebras

### 2014-08-04 Presentation/Prob6.tex
Added example for Artin vs coxeter
Presentation Slides and Diagrams

\newtheorem{proposition}{Proposition}
\newtheorem{rem}{Remark}
\newtheorem{goal}{Goal}

@@

\end{block}

@@

\section{Jacob}

\begin{frame}{Unoriented structures underlying $\Gamma$}
\begin{lemma}
[Lemma 2.2, Barot-Marsh]
For $\Gamma$, if we have a subdiagram of $\Gamma$ with three connected vertices, then the unoriented graph underlying the subdiagram must be one of the following:
\begin{figure}[h]
\centering
\includegraphics[scale = .65]{3vertconnected.PNG}
\caption{Unoriented 3-vertex connected subdiagrams}
\end{figure}
\end{lemma}

\subsection{Possible mutations for 3-cycles in $\Gamma$}

@@

>>>>

\newtheorem{proposition}{Proposition}
\newtheorem{rem}{Remark}
\newtheorem{goal}{Goal}
\newtheorem{Conjecture}{Conjecture}

@@

\end{block}
\end{frame}

\begin{frame}{Example}
\begin{figure}
\centering
\includegraphics[scale=.5]{4cycle.PNG}
\caption{A 4 cycle with edge weights of 1 and 2}
\end{figure}

\small
Coxeter relations:
\begin{itemize}
\item[R1] $s_1^2 = s_2^2 = s_3^2 = s_4^2 = e$
\item[R2] $(s_1s_2)^3 = (s_3s_4)^3 = e$
\item[R2] $(s_2s_3)^4 = (s_4s_1)^4 = e$
\item[R2] $(s_1s_3)^2 = (s_2s_4)^2 = e$
\item[R3] $r(1,2)^2 = r(3,4)^2 = e$, or $(s_1s_2s_3s_4s_3s_2)^2 = (s_3s_4s_1s_2s_1s_4)^2 = e$
\item[R3] $r(2,3)^3 = r(4,1)^3 = e$, or $(s_2s_3s_4s_1s_4s_3)^3 = (s_4s_1s_2s_3s_2s_1)^3 = e$
\end{itemize}
\end{frame}

\begin{frame}{Example}
\begin{figure}
\centering
\includegraphics[scale=.5]{4cycle.PNG}
\caption{A 4 cycle with edge weights of 1 and 2}
\end{figure}

\small
Artin relations:
\begin{itemize}
\item[T2] $\langle s_1, s_2 \rangle ^3 = \langle s_2, s_1 \rangle ^3$, or $s_1s_2s_1 = s_2s_1s_2$
\item[T2] $\langle s_2, s_3 \rangle ^4 = \langle s_3, s_2 \rangle ^4$, or $s_2s_3s_2s_3 = s_3s_2s_3s_2$
\item[T2] $\langle s_2, s_4 \rangle ^2 = \langle s_4, s_2 \rangle ^2$, or $s_2s_4 = s_4s_2$
\end{itemize}
The T2 relations $\langle s_3, s_4 \rangle, \langle s_4, s_1 \rangle, \langle s_1, s_3 \rangle$ can be defined in a similar manner.
\begin{itemize}
\item[T3] $t(1,2) = s_1s_2^{-1}s_3^{-1}s_4s_3s_2s_1^{-1}s_2^{-1}s_3^{-1}s_4^{-1}s_3s_2 = e$, or $s_1s_2^{-1}s_3^{-1}s_4s_3s_2 = s_2^{-1}s_3^{-1}s_4s_3s_2s_1$.
\end{itemize}

The T3 relation $t(3,4) = e$ can be defined in a similar manner.
\end{frame}

@@

\section{Constructing the Isomorphism}

\begin{frame}
In constructing the isomorphsim between $A_{\Gamma}$ and $A_{\Gamma^{\prime}}$, we first prove that $A_{\Gamma} \cong A_{\Gamma^{op}}$, where $\Gamma^{op}$ is the diagram obtained by reversing all arrows in $\Gamma$.
\begin{lemma}
Let A$_{\Gamma}$ be generated by $s_{1}, \dots, s_{n}$, and let A$_{\Gamma^{op}}$ be generated by $r_{1}, \dots, r_{n}$. Then the map $$\Delta: s_{i} \rightarrow r_{i}^{-1}$$ defines an isomorphism between A$_{\Gamma}$ and A$_{\Gamma^{op}}.$
\end{lemma}
\end{frame}

\begin{frame}
Now let $A_{\Gamma}$ be generated by $s_{1}, \dots, s_{n}$ and let $A_{\Gamma^{\prime}}$ be generated by $u_{1}, \dots, u_{n}$. Consider the map $\phi: A_{\Gamma^{\prime}} \rightarrow A_{\Gamma}$ defined as follows:
$$\phi(u_{i}) = 
\begin{cases}
s_{k}s_{i}s_{k}^{-1} &\text{if there is an arrow from i to k in $\Gamma$} \\
s_{i} &\text{otherwise}
\end{cases}$$

\begin{lemma}
The map $\phi$ is a well-defined homomomorphism.
\end{lemma}
\end{frame}

\begin{frame}{Unoriented structures underlying $\Gamma$}
In proving that the map is well-defined, we make use of the fact that diagrams of finite-type have a nice underlying structure. For example, when dealing with the (T2) relations, we have
\begin{lemma}
[Lemma 2.2, Barot-Marsh]
For $\Gamma$ of finite-type, if we have a subdiagram of $\Gamma$ with three connected vertices, then the unoriented graph underlying the subdiagram must be one of the following:
\begin{figure}[h]
\centering
\includegraphics[scale = .65]{3vertconnected.PNG}
\caption{Unoriented 3-vertex connected subdiagrams}
\end{figure}
\end{lemma}

\end{frame}
\subsection{Possible mutations for 3-cycles in $\Gamma$}

@@

\begin{frame}
Now given the maps $\phi$ and $\Delta$, we are able to prove our theorem. Consider the diagram:
\begin{figure}
\includegraphics[scale = .50]{Comm-Diag.pdf}
\end{figure}
One can check that this diagram commutes, and so we find that the map $\phi$ is actually an isomorphism.
\end{frame}

\section{Affine Dynkin Diagrams}
\begin{frame}
It is natural to ask whether a similar result holds for diagrams that are not of finite type. In particular, we will examine diagrams which are mutation equivalent to affine Dynkin diagrams.
\begin{figure}
\includegraphics[scale = .50]{Affine-Diagrams.pdf}
\caption{Affine Dynkin Diagrams}
\end{figure}
\end{frame}

\begin{frame}
In a paper by Felickson and Tumarkin, the authors obtain a similar result for coxeter groups. For a diagram $\Gamma$ of affine type with n+1 nodes, they define a group W$_{\Gamma}$ generated by elements $s_{1}, \dots, s_{n+1}$ and subject to the following relations:

(R1) $s_{i}^{2} = e$ for $i \in \{1, \dots, n\}$.

(R2) $(s_{i}s_{j})^{m_{ij}} = e$ where 
$$m_{ij} = 
\begin{cases}
2 &\text{if there is no arrow between i and j in $\Gamma$} \\
3 &\text{if there is an arrow of weight 1 between i and j in $\Gamma$} \\
4 &\text{if there is an arrow of weight 2 between i and j in $\Gamma$} \\
6 &\text{if there is an arrow of weight 3 between i and j in $\Gamma$} \\
\infty &\text{otherwise}
\end{cases}$$
\end{frame}

\begin{frame}
(R3) For every chordless oriented cycle:
$$i_{0} \stackrel{w_{i_{0}}}{\longrightarrow} i_{1} \stackrel{w_{i_{1}}}{\longrightarrow} \dots \stackrel{w_{i_{d-2}}}{\longrightarrow} i_{d-1} \stackrel{w_{i_{d-1}}}{\longrightarrow} i_{0},$$
define for l $\in \{0, \dots, d-1\}$, 
$$t(l) = (\prod_{j=l}^{l+d-2}{\sqrt{w_{i_{j}}}} - \sqrt{w_{i_{l+d-1}}})^{2}.$$
Then take the relation $(s_{i_{l}}p(i_{l}, i_{l+1}))^{m(l)} = e$ where
$$m(l) =
\begin{cases}
2 &\text{if $t(l)=0$} \\
3 &\text{if $t(l)=1$} \\
4 &\text{if $t(l)=2$} \\
6 &\text{if $t(l)=3$}
\end{cases}$$
\end{frame}

\begin{frame}
(R4) To a subdiagram of the form
\begin{figure}
\includegraphics[scale = .50]{Diagram1.pdf}
\end{figure}
we add the relation $(s_{1}s_{2}s_{3}s_{4}s_{3}s_{2})^{2} = e$.
\end{frame}

\begin{frame}
To a subdiagram of the form 
\begin{figure}
\includegraphics[scale = .50]{Diagram2.pdf}
\end{figure}
we add the relation $(s_{1}s_{2}s_{3}s_{2}s_{1}s_{4}s_{5} \dots s_{n}s_{n+1}s_{n} \dots s_{5}s_{4})^{2} = e$
\end{frame}

\begin{frame}
To a subdiagram of the form
\begin{figure}
\includegraphics[scale = .50]{Diagram3.pdf}
\end{figure}
we add the relations $(s_{2}s_{3}s_{4}s_{1}s_{4}s_{3})^{2} = e$ and $(s_{2}s_{1}s_{4}s_{3}s_{4}s_{1})^{2} = e$.
\end{frame}

\begin{frame}
To a subdiagram of the form
\begin{figure}
\includegraphics[scale = .50]{Diagram4.pdf}
\end{figure}
we add the relation $(s_{n+1}s_{1}s_{n+1}s_{2}s_{3} \dots s_{n-1}s_{n}s_{n-1} \dots s_{3}s_{2})^{2} = e$.
\end{frame}

\begin{frame}
To a subdiagram of the form
\begin{figure}
\includegraphics[scale = .50]{Diagram5.pdf}
\end{figure}
we add the relations $(s_{2}s_{1}s_{2}s_{1}s_{2}s_{3})^{2} = e$ and $(s_{2}s_{3}s_{2}s_{3}s_{2}s_{1})^{2} = e$
\end{frame}

\begin{frame}
\begin{theorem}[Felickson-Tumarkin]
The group $W_{\Gamma}$ is invariant up to isomorphism under diagram mutation.
\end{theorem}
\end{frame}

\begin{frame}
In their paper, Felickson and Tumarkin show that all of the (R4) relations are necessary for this theorem to be true. For example, consider the mutation of \includegraphics[scale = .30]{Diagram2.pdf} at the vertex 1, which is the diagram
\begin{figure}
\includegraphics[scale = .30]{Diagram6.pdf}
\end{figure}
\end{frame}

\begin{frame}
Let $\Gamma$ be a diagram of affine type on n+1 nodes. Then we define $A_{\Gamma}$ to be the group generated by $s_{1}, \dots, s_{n+1}$ satisfying the relations

(T2) $\langle s_{i}, s_{j} \rangle^{m_{ij}} = \langle s_{j}, s_{i} \rangle^{m_{ij}}$ where
$$m_{ij} = 
\begin{cases}
2 &\text{if there is no arrow between i and j in $\Gamma$} \\
3 &\text{if there is an arrow of weight 1 between i and j in $\Gamma$} \\
4 &\text{if there is an arrow of weight 2 between i and j in $\Gamma$} \\
6 &\text{if there is an arrow of weight 3 between i and j in $\Gamma$} \\
\infty &\text{otherwise}
\end{cases}$$
\end{frame}

\begin{frame}
(T3)  For every chordless oriented cycle:
$$i_{0} \stackrel{w_{i_{0}}}{\longrightarrow} i_{1} \stackrel{w_{i_{1}}}{\longrightarrow} \dots \stackrel{w_{i_{d-2}}}{\longrightarrow} i_{d-1} \stackrel{w_{i_{d-1}}}{\longrightarrow} i_{0},$$
define for l $\in \{0, \dots, d-1\}$, 
$$t(l) = (\prod_{j=l}^{l+d-2}{\sqrt{w_{i_{j}}}} - \sqrt{w_{i_{l+d-1}}})^{2}.$$
Then take the relation $\langle s_{i_{l}}p(i_{l}, i_{l+1}) \rangle^{m(l)} = \langle p(i_{l}, i_{l+1})s_{i_{l}} \rangle^{m(l)}$ where
$$m(l) =
\begin{cases}
2 &\text{if $t(l)=0$} \\
3 &\text{if $t(l)=1$} \\
4 &\text{if $t(l)=2$} \\
6 &\text{if $t(l)=3$}
\end{cases}$$
\end{frame}

\begin{frame}
To a subdiagram of the form
\begin{figure}
\includegraphics[scale = .50]{Diagram1.pdf}
\end{figure}
we add the relation $(s_{2}s_{1}s_{2}^{-1})s_{3}^{-1}s_{4}s_{3} = s_{3}^{-1}s_{4}s_{3}(s_{2}s_{1}s_{2}^{-1}).$
\end{frame}

\begin{frame}
To a subdiagram of the form
\begin{figure}
\includegraphics[scale = .50]{Diagram2.pdf}
\end{figure}
we add the relation
$s_{2}(s_{3}^{-1}s_{4}^{-1}\dots s_{n}^{-1}(s_{1}s_{n+1}s_{1}^{-1})s_{n} \dots s_{4}s_{3})$
\newline $= (s_{3}^{-1}s_{4}^{-1}\dots s_{n}^{-1}(s_{1}s_{n+1}s_{1}^{-1})s_{n} \dots s_{4}s_{3})s_{2}$
\end{frame}

\begin{frame}
To a subdiagram of the form
\begin{figure}
\includegraphics[scale = .50]{Diagram3.pdf}
\end{figure}
we add the relations $s_{2}s_{3}^{-1}(s_{4}s_{1}s_{4}^{-1})s_{3} = s_{3}^{-1}(s_{4}s_{1}s_{4}^{-1})s_{3}s_{2}$ and \\
$s_{2}s_{1}s_{4}^{-1}s_{3}s_{4}s_{1}^{-1} = s_{1}s_{4}^{-1}s_{3}s_{4}s_{1}^{-1}s_{2}$.
\end{frame}

\begin{frame}
To a subdiagram of the form
\begin{figure}
\includegraphics[scale = .50]{Diagram4.pdf}
\end{figure}
we add the relation $s_{1}(s_{2}^{-1} \dots s_{n-1}^{-1}(s_{n+1}s_{n}s_{n+1}^{-1})s_{n-1} \dots s_{2}) = (s_{2}^{-1} \dots s_{n-1}^{-1}(s_{n+1}s_{n}s_{n+1}^{-1})s_{n-1} \dots s_{2})s_{1}$.
\end{frame}

\begin{frame}
To a subdiagram of the form
\begin{figure}
\includegraphics[scale = .50]{Diagram5.pdf}
\end{figure}
we add the relations $s_{2}s_{1}^{-1}(s_{2}s_{3}s_{2}^{-1})s_{1} = s_{1}^{-1}(s_{2}s_{3}s_{2}^{-1})s_{1}s_{2}$ and $s_{1}s_{2}s_{3}s_{2}s_{3}^{-1}s_{2}^{-1} = s_{2}s_{3}s_{2}s_{3}^{-1}s_{2}^{-1}s_{1}$.
\end{frame}

\begin{frame}
\begin{Conjecture}
$A_{\Gamma}$ is invariant up to isomorphism under diagram mutation.
\end{Conjecture}
\end{frame}
